\section{Abstract}

The bitcoin protocol has been used for more than a decade, with more than 500m million settled transactions. In order for the system to scale and be able to settle a higher number of transactions it needs to be fundamentally rethought and new technologies need to be developed. This thesis aims to study and develop 
More than 10 years ago the bitcoin protocol set itself to solve the electronic cash problem, being able to make payments in a trust less way, from one party to another, without the need of a third party. 
Now the system has matured and is now being fully taken advantage of, fulfilling what it was initially set to do. But there's only so much the system can scale in its current form, and that is not enough to compete with trust based payment systems like hard cash or payment card networks. The concepts that made bitcoin such an innovative solution at the beginning of its life need to be rethought so it can keep providing what it set itself to do, now at a bigger scale. \\
The lightning network is a bitcoin scaling solution that leverages the trust provided by the bitcoin protocol to create a second layer network that alleviates the intense use that is being given to the bitcoin protocol. It does this by taking the payments "off-chain", excluding the need to register every transaction through the bitcoin protocol, its an elegant solution that takes the form of yet another peer-to-peer network where payments are routed through a series of capacity bounded channels, from a payer to a payee. Part of the process of paying some party through the lightning network is finding a payment path the payment can be routed through. \\
Current solutions take advantage of source routing methods, giving the responsibility of finding the route to the payer with the information it has available. This routes can be found to be invalid, resulting in failed payment attempts and a poor performance of the network. \\
In this work we will define a new way of finding payment routes, one that uses information that is not readily available to the payer and increases the probability of success for payments.